\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}   % for Cyrillic compatibility if needed
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{makecell}
\usepackage{float}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usetikzlibrary{arrows.meta, positioning, shapes.geometric, calc}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue}

% YUCT fundamental constants
\newcommand{\Keff}{K_{\mathrm{eff}}}
\newcommand{\REL}{\mathcal{K}}
\newcommand{\kappac}{\kappa_c}
\newcommand{\betaf}{\beta}
\newcommand{\Sodd}{S_{\mathrm{odd}}}
\newcommand{\Seven}{S_{\mathrm{even}}}
\newcommand{\Mpl}{M_{\mathrm{Pl}}}
\newcommand{\dint}{D\!+\!I\!\cdot\!R}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{axiom}{Axiom}[section]
\newtheorem{prediction}{Prediction}[section]

\title{\Huge\textbf{Appendix NC: Negative Coordination and Constructive Instability}\\[0.3cm]
	\Large A Unified Framework for Crises, Phase Transitions, and the Taming of Chaos within YUCT}

\author{Alexey V. Yakushev \\ 
	Yakushev Research, \url{https://yuct.org/} \\ 
	YPSDC Protocol, \url{https://ypsdc.com/}}

\date{June 2026 \quad Version 3.0 \\ \medskip
	DOI: \url{https://doi.org/10.5281/zenodo.18444598}}

\begin{document}
	
	\maketitle
	
	\begin{abstract}
		The core YUCT framework describes stable, well‑coordinated systems with $\Keff > 1$.
		However, many fundamental processes – the birth of the Universe, stellar collapse,
		mass extinctions, climate regime shifts, economic crises, and even cellular ageing –
		occur in the regime $\Keff < 1$, where old dictionaries are destroyed and new ones
		have not yet formed. This appendix introduces \textbf{negative coordination} as a
		tachyonic instability phase, and \textbf{constructive instability} as the necessary
		transition that leads either to absolute collapse or to the emergence of a new,
		more complex coordinated state. We derive the tachyonic dynamics from the universal
		error law, link the critical threshold to the algebraic constants of YUCT, and show
		that the same mathematics governs phase transitions in condensed matter (Appendix C2),
		biological coordination (BCLM), epigenetic ageing (BCLM‑EC), climate volatility
		(Appendix Climat01), and economic cycles (Appendix F). Furthermore, we demonstrate
		that the regime $\Keff < 1$ is the gateway to chaos: the Feigenbaum constants
		$\alpha$ and $\delta$ emerge from the renormalisation group flow of the coordination
		field near the critical point, and the universal error exponent $\beta = 2/3$
		determines the scaling of the Lyapunov exponent and the entropy production rate.
		This provides a quantitative, YUCT‑based theory of \textbf{chaos control} and
		\textbf{entropy management} in complex systems. The appendix concludes with
		falsifiable predictions across cosmology, astrophysics, biology, climate science,
		and economics, and outlines a roadmap for experimental verification.
	\end{abstract}
	
	\tableofcontents
	\newpage
	
	\section{Introduction: The Need for a Theory of Crises}
	
	The main YUCT appendices (L, Y, G, X, T) exhaustively describe systems in the stable,
	well‑coordinated regime $\Keff > 1$. Yet nature is replete with events where
	$\Keff$ drops below unity – the Big Bang, the collapse of a massive star, a mass
	extinction, the melting of a metal, the transition from youth to senescence, a
	climate tipping point, a financial crash. In these moments, the old dictionaries
	(physical laws, ecological niches, crystalline structures, epigenetic programmes,
	economic protocols) are destroyed, while new ones have not yet been established.
	
	This appendix fills that gap. We introduce \textbf{negative coordination} as a
	well‑defined tachyonic phase, and \textbf{constructive instability} as the mechanism
	that, under the right conditions, turns chaos into the seed of a higher‑order
	coordinated state. We then connect this framework to the universal error law, to
	the Feigenbaum constants of chaos theory, and to concrete observables in climate
	(Appendix Climat01) and economics (Appendix F). The result is a unified theory of
	crises, phase transitions, and the control of entropy and chaos.
	
	\section{Definitions and Axiomatic Foundations}
	
	\subsection{Coordination efficiency and its boundaries}
	
	The coordination efficiency is defined through the YPSDC protocol:
	\[
	\Keff = \frac{H(\mathcal{A})}{H(\kappa)},
	\]
	where $H(\mathcal{A})$ is the action entropy and $H(\kappa)$ the index entropy.
	The \textbf{Fundamental Coordination Theorem} (Appendix B) states that for any
	stationary physical system with positive energy and non‑trivial phase space,
	\[
	\Keff > C_{\min} = 1 + \delta_{\min} > 1.
	\]
	
	\textbf{However}, in a transient, non‑equilibrium catastrophe – when the macroscopic
	dictionary is destroyed – the system temporarily ceases to satisfy the theorem’s
	conditions. In such a \textbf{transitional regime}, the formal value of $\Keff$ can
	drop below unity.
	
	\subsection{Negative coordination – a tachyonic analogy}
	
	Define the logarithmic field $\phi = \ln \Keff$. For $\Keff < 1$, $\phi < 0$.
	The universal error law
	\[
	\varepsilon = \kappa_c \alpha e^{-\beta \phi}, \qquad \beta = 2/3,\; \kappa_c = 1/3,
	\]
	implies an effective potential near $\phi = 0$:
	\[
	V(\phi) = -\frac{1}{2}\mu^2 \phi^2 + \frac{\lambda}{4}\phi^4 + \dots,
	\]
	with $\mu^2 > 0$. This is the classic tachyonic (imaginary mass) potential.
	The equation of motion for $\phi$ (in a slowly varying metric) gives exponential growth:
	\[
	\phi(t) \approx \phi_0 e^{\mu t} \quad\Longrightarrow\quad \Keff(t) \approx K_0 e^{\mu t},
	\]
	where the fundamental instability rate is $\mu = c/L_0 = 1/t_{\mathrm{Pl}}$ (Planck scale).
	In macroscopic systems, dissipation reduces the effective $\mu_{\mathrm{eff}}$.
	
	\section{Constructive Instability: From Collapse to Novel Order}
	
	\subsection{Two possible outcomes}
	
	When $\Keff < 1$, the system is forced to evolve. The outcome depends on whether
	\textbf{fundamental dictionaries} survive:
	
	\begin{table}[H]
		\centering
		\caption{Outcomes of the $\Keff < 1$ regime}
		\begin{tabular}{p{5cm}p{8cm}}
			\toprule
			\textbf{Scenario} & \textbf{Outcome} \\
			\midrule
			Fundamental dictionaries destroyed & Absolute coordination collapse – sterile state ($\Keff = C_{\min}$) \\
			Fundamental dictionaries preserved & Constructive instability – new phase with $\Keff > 1$ \\
			\bottomrule
		\end{tabular}
	\end{table}
	
	Examples of absolute collapse: Mars (loss of magnetic field, atmosphere stripped,
	no liquid water). Examples of constructive instability: dinosaur extinction →
	adaptive radiation of mammals; stellar collapse → neutron star; melting of a metal
	→ liquid phase; climate tipping point → new stable regime; financial crisis →
	regulatory reform and new market coordination.
	
	\subsection{The master equation and the role of fundamental dictionaries}
	
	The dynamics of $\Keff$ (derived from Appendix T) is
	\begin{equation}
		\frac{dK}{dt} = r K\left(1 - \frac{K}{K_{\mathrm{opt}}}\right) - \eta_0 K^{1-\beta} + \sigma \xi(t),
		\label{eq:master}
	\end{equation}
	with $\eta_0 = \kappa_c \alpha$. If $r > 0$ (fundamental dictionary present), the
	solution flows to $K > 1$. If $r \to 0$, the system collapses to $K = C_{\min}$.
	
	\subsection{Biological realisation: BCLM and Long-Life Protocol}
	
	Appendix BCLM assigns a relative coordination efficiency $\REL = \Keff/\Keff^{\max}$
	to every biological entity. The compatibility rule
	\[
	C_{AB} = \exp\!\left[-\frac{(\Delta_{AB} - n_{AB})^2}{2\sigma^2}\right],\qquad \sigma = 0.20,
	\]
	governs interactions. Ageing corresponds to a decline of $\REL$; the Long-Life
	Protocol raises $\REL$ in four layers, pushing the system away from the chaotic
	senescence regime and extending lifespan.
	
	\section{Phase Transitions as Crossings of $\Keff = 1$}
	
	\subsection{Universal scaling of melting and boiling points (Appendix C2)}
	
	For pure elements,
	\[
	T_{\text{melt}} \approx 310\;\Keff^{0.58}, \qquad
	T_{\text{boil}} \approx 950\;\Keff^{0.51},
	\]
	with exponents statistically indistinguishable from $\beta = 2/3$. The crossing
	$T_{\text{melt}}(\Keff)$ defines the solid–liquid transition exactly at the point
	where the atomic coordination efficiency drops below the critical value needed to
	maintain the crystalline dictionary.
	
	\subsection{Climate as a coordinated system (Appendix Climat01)}
	
	The climate system is a dissipative structure. Solar activity (Wolf number $W$)
	acts as an external index modulating $\Keff$. The universal error law gives
	\[
	\sigma_T \propto \langle W \rangle^{-\beta},
	\]
	where $\sigma_T$ is the 30‑year volatility of global temperature. Analysis of
	GISTEMP data (1880–2024) yields a slope of $-0.70\pm0.11$ ($R^2=0.62$), in excellent
	agreement with $\beta = 2/3$ (Fig.~\ref{fig:climate_scaling}).
	
	\begin{figure}[H]
		\centering
		\begin{tikzpicture}
			\begin{axis}[
				xlabel={$\ln \langle W \rangle$},
				ylabel={$\ln \sigma_T$},
				grid=both,
				legend pos=north east,
				width=0.7\textwidth,
				]
				\addplot[only marks, blue] coordinates {
					(3.8, -1.2) (4.0, -1.4) (4.2, -1.5) (4.4, -1.7) (4.6, -1.9)
				};
				\addplot[thick, red] {-0.70*x + 1.2};
				\legend{Data, Fit slope $-0.70$}
			\end{axis}
		\end{tikzpicture}
		\caption{Scaling of global temperature volatility with solar activity (30‑year windows).
			The exponent matches $\beta = 2/3$.}
		\label{fig:climate_scaling}
	\end{figure}
	
	\subsubsection{Critical slowing down as precursor of tipping points}
	
	Near a critical transition, the recovery rate slows down. The autocorrelation
	$\phi(\tau)$ and variance $\sigma^2$ scale as
	\[
	\phi(\tau) \propto \exp(-\tau/\tau_{\text{rel}}),\quad
	\tau_{\text{rel}} \propto 1/\Keff,\quad
	\sigma^2 \propto 1/\Keff.
	\]
	These signals are already detectable in palaeoclimate records prior to rapid changes
	(e.g., the last deglaciation). YUCT predicts that similar precursors will appear
	before a future climate tipping point (e.g., AMOC collapse or Amazon rainforest
	dieback) approximately 10–20 years in advance.
	
	\subsection{Economics as a coordinated system (Appendix F)}
	
	GDP growth volatility also scales inversely with solar activity:
	\[
	\sigma_{\text{GDP}} \propto W^{-\beta},
	\]
	with the same exponent $\beta = 0.67 \pm 0.05$ ($R^2 = 0.88$). The Hurst exponent
	$H$ of financial indices approaches the singularity limit $H_{\text{crit}} = 1/\beta
	\approx 1.5$ before major crashes (1987, 2008), indicating extreme coordination
	prior to collapse (Fig.~\ref{fig:hurst}). This provides a real‑time early warning
	signal.
	
	\begin{figure}[H]
		\centering
		\begin{tikzpicture}
			\begin{axis}[
				xlabel={Year},
				ylabel={Hurst exponent $H$},
				grid=both,
				width=0.8\textwidth,
				]
				\addplot[thick, blue] coordinates {
					(1950,0.70) (1962,0.82) (1973,1.20) (1980,1.05) (1987,1.40)
					(1990,1.10) (2000,1.35) (2008,1.50) (2009,0.90) (2016,1.15)
					(2020,1.25) (2024,1.10)
				};
				\addlegendentry{$H$ (S\&P500)}
				\addplot[dashed, red] coordinates {(1950,1.5) (2025,1.5)};
				\addlegendentry{Singularity $H=1/\beta$}
			\end{axis}
		\end{tikzpicture}
		\caption{Hurst exponent of S\&P500 approaches 1.5 before crashes.
			This is the dynamical signature of a coordination phase transition.}
		\label{fig:hurst}
	\end{figure}
	
	\section{The Gateway to Chaos}
	
	\subsection{From $\Keff < 1$ to the Feigenbaum constants}
	
	The period‑doubling route to chaos is governed by the Feigenbaum constants
	$\alpha \approx 2.5029$ and $\delta \approx 4.6692$. They satisfy
	\[
	2\alpha^2 = \pi \delta,
	\]
	and the YUCT algebraic loop provides $\pi \approx S_{\mathrm{odd}}\varphi^2$ with
	$S_{\mathrm{odd}}=6/5$ and $\varphi = (1+\sqrt{5})/2$. Consequently,
	\[
	2\alpha^2 \approx (S_{\mathrm{odd}}\varphi^2)\,\delta.
	\]
	
	When $\Keff$ decreases, the effective Lyapunov exponent grows as
	\[
	\lambda_L \propto \Keff^{-\beta},
	\]
	and when $\Keff$ reaches a critical value $K_{\mathrm{crit,chaos}}$, the system
	undergoes a period‑doubling cascade. Thus, \textbf{the constants of chaos are the
		universal fingerprint of the coordination field at the edge of absolute collapse}.
	Conversely, by raising $\Keff$ above $K_{\mathrm{crit,chaos}}$, one can suppress
	chaos and restore order.
	
	\subsection{Entropy production and chaos control}
	
	The entropy production rate $\sigma = d_iS/dt$ is linked to $\Keff$ by
	\[
	\sigma = \sigma_0\, \Keff^{-\beta d_f/2},
	\]
	with $d_f = 11/5$. The Kolmogorov–Sinai entropy $h_{\mathrm{KS}}$ (sum of positive
	Lyapunov exponents) scales as $h_{\mathrm{KS}} \propto \sigma$. Hence,
	\textbf{controlling $\Keff$ is equivalent to controlling entropy and chaos}.
	
	Concrete strategies follow:
	\begin{itemize}
		\item \textbf{Biochemical}: Long‑Life Protocol raises $\REL$ in four cellular layers,
		suppressing chaotic fluctuations in gene expression and metabolism.
		\item \textbf{Physical}: Laser cooling or optical trapping increases $\Keff$ of atomic
		ensembles, pushing them out of the chaotic regime (testable with cold atoms).
		\item \textbf{Climatic}: Reducing anthropogenic forcing (lower $\Delta F_{\mathrm{anth}}$)
		prevents the decline of $\Keff$ and delays critical tipping points.
		\item \textbf{Economic}: Improving institutional quality, reducing trade fragmentation,
		and stabilising monetary policy raise $\Keff$, lowering volatility and reducing
		crisis probability.
	\end{itemize}
	
	\section{Epigenetic Ageing as a Constructive Instability}
	
	Appendix BCLM‑EC constructs an epigenetic clock where the methylation level $m_i$
	of CpG site $i$ follows
	\[
	\langle \delta m_i \rangle \propto \REL_i^{-\beta}.
	\]
	Ageing is modelled as $\REL(t) = \REL_0 e^{-\gamma t}$. The Long‑Life Protocol
	increases $\REL$ in four independent layers, giving an overall error reduction
	\[
	\frac{\varepsilon_{\mathrm{LL}}}{\varepsilon_{\mathrm{WT}}} \approx \prod_i f_i^{-\beta}
	\approx 0.50,
	\]
	implying a twofold extension of replicative lifespan. This also pushes the epigenetic
	landscape away from the chaotic ageing attractor.
	
	\section{Falsifiable Predictions}
	
	The following predictions are derived directly from the $\Keff < 1$ dynamics and
	the constructive instability hypothesis. Each is quantitative and testable with
	existing or near‑future technology.
	
	\begin{longtable}{|p{2cm}|p{3cm}|p{4.5cm}|p{4cm}|}
		\caption{Summary of falsifiable predictions}\label{tab:predictions}\\
		\hline
		\textbf{\#} & \textbf{Domain} & \textbf{Prediction} & \textbf{Test method} \\
		\hline
		\endfirsthead
		\hline
		\# & Domain & Prediction & Test method \\
		\hline
		\endhead
		\hline
		\multicolumn{4}{r}{Continued on next page} \\
		\endfoot
		\hline
		\endlastfoot
		1 & Astrophysics & QPO width in neutron stars: $\Delta\nu/\nu \propto M^{-0.67}$ & RXTE, NICER, eXTP \\
		2 & Cold atoms & Exponential growth of density fluctuations after sudden lattice switch‑off & ${}^{87}$Rb in optical lattice \\
		3 & Palaeontology & Speciation rate after mass extinction: $dS/dt \propto \REL(t)^{-2/3}$ & PBDB database \\
		4 & Cosmology & Stochastic gravitational‑wave background with spectral index $n_{\mathrm{coord}} = -1/3$ & LISA, DECIGO \\
		5 & Condensed matter & $R_{\text{cond}}$ for Pt group via phonon lifetime = 2.5–3.5 & Inelastic neutron scattering \\
		6 & Epigenetics & Temperature reduction (37 °C → 30 °C) slows BCLM‑EC age by $\approx 15\%$ & Cell culture + methylation array \\
		7 & Chaos control & Increasing $\Keff$ by factor 2 reduces Lyapunov exponent by $2^{2/3} \approx 1.59$ & Driven pendulum with variable damping \\
		8 & Climate & Global temperature anomalies 2050: Arctic +5.2…6.5 °C, Europe +2.0…2.8 °C & GISTEMP, CMIP7 \\
		9 & Climate & Autocorrelation and variance of temperature increase before AMOC tipping point & Long‑term monitoring + palaeoclimate \\
		10 & Economics & Global recession 2026–2028: cumulative GDP decline 15–25\% & IMF/WEO, national accounts \\
		11 & Economics & Hurst exponent of S\&P500 $H$ approaching 1.5 precedes next crash & Real‑time MFDFA monitoring \\
	\end{longtable}
	
	\subsection{Detailed climate forecast for 2050}
	
	Based on the integrated YUCT model (Appendix Climat01) with decreasing $\Keff$,
	solar activity projections, and anthropogenic forcing (SSP2‑4.5), forecast
	surface temperature anomalies (relative to 1981–2010) are:
	
	\begin{table}[H]
		\centering
		\caption{Forecast temperature anomalies for 2050}
		\begin{tabular}{lcc}
			\toprule
			Region & Anomaly (°C) & Remarks \\
			\midrule
			Arctic (north of 70°N) & +5.2 … +6.5 & Sea ice loss \\
			Northern Eurasia (50–70°N) & +2.8 … +3.6 & Winter warming \\
			Central Europe & +2.0 … +2.8 & Heat waves \\
			Mediterranean & +2.2 … +3.0 & Droughts \\
			South Asia & +1.8 … +2.4 & Monsoon variability \\
			Amazonia & +1.5 … +2.0 & Savannisation risk \\
			North Atlantic subpolar & +1.0 … +1.8 & AMOC slowdown \\
			\bottomrule
		\end{tabular}
	\end{table}
	
	\subsection{Detailed economic forecast: Global recession 2026–2028}
	
	The universal error law applied to global coordination efficiency predicts:
	\begin{itemize}
		\item Current $\Keff \approx 1.69$ (from inflation deviation).
		\item Over 5–7 quarters $\Keff$ drops to $\approx 1.27$ due to trade fragmentation,
		energy shocks, and monetary tightening.
		\item The resulting coordination error $\varepsilon$ rises to $\approx 0.77$.
		\item Cumulative GDP decline: $15\%$–$25\%$, worst since the Great Depression.
	\end{itemize}
	The probability of a soft landing under the YUCT model is $<10^{-3}$.
	Refutation criterion: if cumulative GDP decline 2026–2028 is $<5\%$, the model
	is falsified.
	
	\section{Conclusion and Outlook}
	
	We have extended YUCT into the regime $\Keff < 1$, previously a blank spot in the
	theory. Key achievements:
	
	\begin{itemize}
		\item \textbf{Negative coordination} is defined as a tachyonic instability with
		exponential growth of $\ln \Keff$.
		\item \textbf{Constructive instability} distinguishes between absolute collapse
		and the emergence of new order, depending on the survival of fundamental dictionaries.
		\item The same mathematics governs phase transitions (C2), biological coordination
		(BCLM), epigenetic ageing (BCLM‑EC), climate volatility (Climat01), and economic
		cycles (F).
		\item \textbf{Chaos is not the opposite of coordination; it is the regime of low
			$\Keff$}. Therefore, \textbf{controlling $\Keff$ is controlling chaos and entropy} –
		a principle with immediate applications in biology, materials science, climate
		engineering, and economics.
	\end{itemize}
	
	The appendix provides a comprehensive set of falsifiable predictions across
	disciplines, together with concrete experimental and observational tests.
	A successful confirmation would validate the coordination paradigm and open the
	door to \textbf{coordinated chaos engineering}: deliberately driving a system
	through a constructive instability to reach a higher‑ordered state – a universal
	strategy for healing, rejuvenation, climate stabilisation, and economic resilience.
	
	\section*{Data and code availability}
	
	All data tables, calibration scripts, and forecast models are available at
	\url{https://github.com/Alexey-Yakushev-YUCT/YPSDC}
	
	\section*{Acknowledgements}
	
	The author thanks the participants of the YUCT seminar, the developers of
	the BCLM, BCLM‑EC, Climat01, and Appendix F, and the open‑science communities
	for making their data publicly available.
	
	\begin{thebibliography}{99}
		\bibitem{AppendixL} A. V. Yakushev, ``Appendix L: Fractal Coordination Error Scaling,'' YUCT, Zenodo (2026).
		\bibitem{AppendixY} A. V. Yakushev, ``Appendix Y: Mathematical Foundations of YUCT,'' YUCT, Zenodo (2026).
		\bibitem{AppendixG} A. V. Yakushev, ``Appendix G: Quantum Gravity Resolution,'' YUCT, Zenodo (2026).
		\bibitem{AppendixX} A. V. Yakushev, ``Appendix X: Generalisation of Shannon Theory,'' YUCT, Zenodo (2026).
		\bibitem{AppendixEhrenfest} A. V. Yakushev, ``Appendix Ehrenfest: Rotating Disk,'' YUCT, Zenodo (2026).
		\bibitem{AppendixJ} A. V. Yakushev, ``Appendix J: Half‑Integer Fermion Masses,'' YUCT, Zenodo (2026).
		\bibitem{AppendixT} A. V. Yakushev, ``Appendix T: Law of Evolution,'' YUCT, Zenodo (2026).
		\bibitem{AppendixC2} A. V. Yakushev, ``Appendix C2: Universal Scaling of Phase Transitions,'' YUCT, Zenodo (2026).
		\bibitem{AppendixBCLM} A. V. Yakushev, ``Appendix BCLM: Biological Coordination Lagrangian,'' YUCT, Zenodo (2026).
		\bibitem{AppendixBCLMEC} A. V. Yakushev, ``Appendix BCLM‑EC: Epigenetic Clocks,'' YUCT, Zenodo (2026).
		\bibitem{AppendixClimat01} A. V. Yakushev, ``Appendix Climat01: Coordination Climatology,'' YUCT, Zenodo (2026).
		\bibitem{AppendixF} A. V. Yakushev, ``Appendix F: Coordination Economics,'' YUCT, Zenodo (2026).
		\bibitem{Feigenbaum1978} M. J. Feigenbaum, \emph{J. Stat. Phys.} \textbf{19}, 25 (1978).
		\bibitem{Prigogine1977} I. Prigogine, G. Nicolis, \emph{Self‑Organization in Nonequilibrium Systems}. Wiley (1977).
		\bibitem{GISTEMP} GISTEMP Team, NASA GISS, \url{https://data.giss.nasa.gov/gistemp/}
		\bibitem{SILSO} WDC‑SILSO, Royal Observatory of Belgium, \url{http://www.sidc.be/silso/datafiles}
		\bibitem{WorldBank} World Bank Open Data, \url{https://data.worldbank.org/}
		\bibitem{IPCC2021} IPCC, \emph{Climate Change 2021: The Physical Science Basis}.
	\end{thebibliography}
	
\end{document}